---
title: "Explore famous psychological schools"
author: "Jiahao Shao"
date: "2022/2/1"
output:
  html_notebook: default
  html_document: default
---


<center><span style="font-size:15px;"><font face="Times New Roman">*The ultimate value of life depends upon awareness and the power of contemplation rather than upon mere survival.*</front></span></center>

<span style="font-size:15px;"><p align="right">*By Aristotle*</p></span>

<span style="font-size:19px;">The above quote is said by Aristotle, a well-known Greek philosopher and polymath in Ancient Greek. He has achievements in many fields, like math, physics, and especially, philosophy. He explored the relationship between humans and nature. Aristotle’s works and the philosophy school of Aristotle shaped centuries of philosophy from Late Antiquity through the Renaissance, and even today continue to be studied with ardent interest.[1]</span>

<div align=center><img width = '224' height ='300' src ="../figs/Aristotle_Altemps_Inv8575.jpg"></div>

<center>a Greek bronze bust of Aristotle[2]</center>

<span style="font-size:19px;">Then we want to take a deeper look at the sentences Aristotle said and find the most frequent words he has mentioned. Here we would use a dataset from Philosophy Data Project.[3] The dataset contains over 300,000 sentences from over 50 texts spanning ten major schools of philosophy, including Aristotle. We import the dataset, do the data cleaning, ignore the punctuation as well as some common words, and finally, make a word cloud.</span>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  warning=FALSE,
  error=FALSE
)

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# R Libraries
library(ggplot2)
library(tm)
library(wordcloud)
library(SnowballC)
library(RColorBrewer)
library(dplyr)
library(tidytext)
library(knitr)

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
phi <- read.csv("D:/OneDrive/Documents/5243/data/philosophy_data.csv", stringsAsFactors = F, encoding = "UTF-8")
#phi_backup <- phi
#phi <- phi_backup
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# Aristotle
phi_ari <- phi[phi$school == "aristotle",]
phi_ari

#content <- iconv(phi_com$lemmatized_str, to = "UTF-8")
content <- Corpus(VectorSource(phi_ari$sentence_str))

content = tm_map(content, content_transformer(tolower))
content = tm_map(content, removeNumbers)
content = tm_map(content, removePunctuation)
content = tm_map(content, removeWords, c("the", "and", "-pron-", "one", "will", "can", "may", "must", "say", "man" ,stopwords("english"))) 
content =  tm_map(content, stripWhitespace)


# use tf-idf instead of freq
content_dtm_tfidf <- DocumentTermMatrix(content, control = list(weighting = weightTfIdf))
content_dtm_tfidf = removeSparseTerms(content_dtm_tfidf, 0.97)
#inspect(content_dtm_tfidf[1,1:20])
freq = data.frame(sort(colSums(as.matrix(content_dtm_tfidf)), decreasing=TRUE))

```

\tiny
```{r, message=FALSE, warning=FALSE, echo=FALSE}
wordcloud(rownames(freq), freq[,1], max.words=100, random.order=FALSE,rot.per=0.2,colors=brewer.pal(9,"Dark2"))
```

\normalsize
<span style="font-size:19px;">The above figure shows the frequency of the words from Aristotle. We can see that "things" has the most frequency, followed by "also", "animals", "nature", "body", etc. That makes sense because Aristotle does explore the relationship between different things, like humans and nature.</span>

<span style="font-size:19px;">Next, we will do something more interesting. Let's talk about the word frequency of two most well-known schools, ***Communism*** and ***Capitalism***.</span>

<span style="font-size:19px;">Let's begin with ***Communism*** :</span>

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# Communism
phi_com <- phi[phi$school == "communism",]
phi_com

#content <- iconv(phi_com$lemmatized_str, to = "UTF-8")
content <- Corpus(VectorSource(phi_com$sentence_str))

content = tm_map(content, content_transformer(tolower))
content = tm_map(content, removeNumbers)
content = tm_map(content, removePunctuation)
content = tm_map(content, removeWords, c("the", "and", "-pron-", "one", "will", "can", "may", "must", "say", "man" ,stopwords("english"))) 
content =  tm_map(content, stripWhitespace)


# use tf-idf instead of freq
content_dtm_tfidf <- DocumentTermMatrix(content, control = list(weighting = weightTfIdf))
content_dtm_tfidf = removeSparseTerms(content_dtm_tfidf, 0.97)
#inspect(content_dtm_tfidf[1,1:20])
freq = data.frame(sort(colSums(as.matrix(content_dtm_tfidf)), decreasing=TRUE))

```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
wordcloud(rownames(freq), freq[,1], max.words=100, random.order=FALSE,rot.per=0.2,colors=brewer.pal(9,"Dark2"))
```

<span style="font-size:19px;">Here is the word cloud for Communism. The figure is much different than the last one. Not surprisingly, "labour" is the biggest word, meaning that the communists mentioned this word more than any other word. We all know that Communists care about labor, and the figure shows the pattern.</span> 

<span style="font-size:19px;">Then, let's see the word cloud for ***Capitalism*** :</span>

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# Capitalism
phi_cap <- phi[phi$school == "capitalism",]
phi_cap

content <- Corpus(VectorSource(phi_cap$sentence_str))

content = tm_map(content, content_transformer(tolower))
content = tm_map(content, removeNumbers)
content = tm_map(content, removePunctuation)
content = tm_map(content, removeWords, c("the", "and", "pron", "one", "will", "can", "may", "must", "say", "man" ,stopwords("english"))) 
content =  tm_map(content, stripWhitespace)


# use tf-idf instead of freq
content_dtm_tfidf <- DocumentTermMatrix(content, control = list(weighting = weightTfIdf))
content_dtm_tfidf = removeSparseTerms(content_dtm_tfidf, 0.96)
#inspect(content_dtm_tfidf[1,1:20])
freq = data.frame(sort(colSums(as.matrix(content_dtm_tfidf)), decreasing=TRUE))

```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
wordcloud(rownames(freq), freq[,1], max.words=100, random.order=FALSE,rot.per=0.2,colors=brewer.pal(9,"Dark2"))
```

<span style="font-size:19px;">We can see that "price" is the largest, followed by "upon" and 'money". We can also see that "trade", "tax", ""quantity", and "rent" in the figure, which do not show in the Coummism.</span>

<span style="font-size:19px;">Therefore, creating a word cloud and explore the results can be a good way to get a better understanding of different philosophy schools.</span>

<span style="font-size:19px;">Finally, I'll leave a word cloud for continental philosophy, which had been prevalent from the early 20th century in England and later in  other English-speaking countries. Can you find anything interesting from the graph? Leave a comment about what you found!</span>

<span style="font-size:19px;"> ***Continental*** :</span>
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# continental
phi_cont <- phi[phi$school == "continental",]
phi_cont

content <- Corpus(VectorSource(phi_cont$sentence_str))

content = tm_map(content, content_transformer(tolower))
content = tm_map(content, removeNumbers)
content = tm_map(content, removePunctuation)
content = tm_map(content, removeWords, c("the", "and", "pron", "one", "will", "can", "may", "must", "say", "man" ,stopwords("english"))) 
content =  tm_map(content, stripWhitespace)


# use tf-idf instead of freq
content_dtm_tfidf <- DocumentTermMatrix(content, control = list(weighting = weightTfIdf))
content_dtm_tfidf = removeSparseTerms(content_dtm_tfidf, 0.98)
#inspect(content_dtm_tfidf[1,1:20])
freq = data.frame(sort(colSums(as.matrix(content_dtm_tfidf)), decreasing=TRUE))

```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
wordcloud(rownames(freq), freq[,1], max.words=100,max_font_size=20, random.order=FALSE,rot.per=0.2,colors=brewer.pal(9,"Dark2"))

```


<span style="font-size:19px;">***Reference***</span>

[1]	Malpas, J., Donald Davidson, The Stanford Encyclopedia of Philosophy (Winter 2012 Edition), Edward N. Zalta (ed.), URL = https://plato.stanford.edu/archives/win2012/entries/davidson/.

[2] picture from: https://upload.wikimedia.org/wikipedia/commons/a/ae/Aristotle_Altemps_Inv8575.jpg.

[3] dataset from: https://www.kaggle.com/kouroshalizadeh/history-of-philosophy






















